
# This is a network report generated on `r format(Sys.time(), "%Y-%m-%d %H-%M-%S")`
# by `r Sys.info()['login']` with `r version$version.string`
# on a `r version$platform` platform.

This report is based on the file `r basename(cc.file)` in directory **`r dirname(cc.file)`**.



```{r, include=FALSE}
library('Matrix')

in.dir <- dirname(cc.file)

load(cc.file)
load(gsub('combinedconf', 'betas', cc.file))
load(paste(in.dir, 'params_and_input.RData', sep='/'))

if (is.null(colnames(comb.confs))) {
  colnames(comb.confs) <- IN$tf.names
  rownames(comb.confs) <- rownames(IN$exp.mat)
}

beta.sign <- as.matrix(betas[[1]] * 0)
for (n in 1:length(betas)) {
  beta.sign <- beta.sign + sign(betas[[n]])
}
dimnames(beta.sign) <- dimnames(comb.confs)

# match the ccfile to the prior that was used
  p.ind <- which(sapply(names(IN$priors), function(n) grepl(n, cc.file)))
  p.name <- names(IN$priors)[p.ind]
  p.mat <- IN$grouped.pred[[p.name]]$prior.mat[rownames(beta.sign), colnames(beta.sign)]

# get median rescaled beta
resc.betas <- lapply(betas.resc, function(x) x[beta.sign != 0])
resc.betas <- matrix(unlist(resc.betas), length(resc.betas[[1]]))
resc.betas.median <- apply(resc.betas, 1, median)

# create data frame of non-zero scores 
non.zero <- which(beta.sign != 0, arr.ind=TRUE)
vec.ind <- which(beta.sign != 0)
net.df <- data.frame(regulator=colnames(beta.sign)[non.zero[, 2]], 
                     target=rownames(beta.sign)[non.zero[, 1]], 
                     beta.sign=beta.sign[vec.ind], 
                     var.exp.median=resc.betas.median,
                     prior=p.mat[vec.ind],
                     vec.ind=vec.ind)
                     
var.exp <- as.matrix(betas.resc[[1]] * 0)
var.exp[net.df$vec.ind] <- net.df$var.exp.median
                     
VAR.EXP.TH <- 0.2
BETA.SIGN.TH <- 0.75 * PARS$num.boots


net.stats <- function(prior.mat) {
  cat('prior.mat.stats\n')
  cat('non-zero entries:\t')
  edges <- sum(prior.mat != 0)
  cat(edges, '\n')
  cat('TFs with targets:\t')
  tfs <- sum(apply(prior.mat != 0, 2, sum) > 0)
  cat(tfs, '\n')
  cat('genes with regulators:\t')
  targets <- sum(apply(prior.mat != 0, 1, sum) > 0)
  cat(targets, '\n')
  cat('average out degree:\t', edges / tfs, '\n')
  cat('average in degree:\t', edges / targets, '\n')
}
```

Time used for this network inference run (in hours): 
```{r, echo=FALSE}
print(round(PROCTIME/3600, 2))
```

# Inferred net based on beta sign threshold

Table of the sign of interactions added across all `r PARS$num.boots` bootstraps.
```{r}
bsv <- as.vector(beta.sign)

table(bsv)
plot(table(bsv[abs(bsv) >= BETA.SIGN.TH]))

# total nuber of interactions
sum(abs(bsv) >= BETA.SIGN.TH)

# table of out-degree and counts
out.tab <- table(subset(net.df, abs(beta.sign) >= BETA.SIGN.TH)$regulator)
table(out.tab)
# show how many regulators (TFs) have targets
table(out.tab > 0)

# print the regulators with the most targets
head(sort(out.tab, decreasing=TRUE))

# table of in-degree and counts
in.tab <- table(subset(net.df, abs(beta.sign) >= BETA.SIGN.TH)$target)
table(in.tab)
# show how many targets have at least one regulator
table(in.tab > 0)

# print the targets with most regulators
head(sort(in.tab, decreasing=TRUE))

# dimensionality of input expression
dim(IN$exp.mat)
```


# Inferred net based on explained variance threshold
```{r}
# how does the median explained variance compare to the beta sign
require('ggplot2')
g <- ggplot(net.df, aes(x=factor(beta.sign), y=var.exp.median)) + geom_boxplot() + geom_hline(yintercept=VAR.EXP.TH, color='red')
plot(g)

ia.order <- order(net.df$var.exp.median, decreasing=TRUE)
tmp <- subset(net.df[ia.order, ], var.exp.median >= 0.1)
plot(tmp$var.exp.median, 1:nrow(tmp), 'l', xlab='variance explained threshold', ylab='number of interactions in network')
abline(v=VAR.EXP.TH, col='red')

vev <- as.vector(net.df$var.exp.median)
table(cut(vev, 20))

vev.b <- cut(vev, 20)
.pardefault <- par(no.readonly = T)
par(mar=c(8,4,2,1))
plot(as.vector(table(vev.b, exclude=levels(vev.b)[1])), pch=19, xaxt='n', xlab='', ylab='counts', main='explained variance')
axis(1, at=1:(length(levels(vev.b))-1), labels=levels(vev.b)[-1], las=2)
par(.pardefault)



# total nuber of interactions
sum(vev >= VAR.EXP.TH)

# table of out-degree and counts
out.tab <- table(subset(net.df, var.exp.median >= VAR.EXP.TH)$regulator)
table(out.tab)
# show how many regulators (TFs) have targets
table(out.tab > 0)

# print the regulators with the most targets
head(sort(out.tab, decreasing=TRUE))

# table of in-degree and counts
in.tab <- table(subset(net.df, var.exp.median >= VAR.EXP.TH)$target)
table(in.tab)
# show how many targets have at least one regulator
table(in.tab > 0)

# print the targets with most regulators
head(sort(in.tab, decreasing=TRUE))


```

# Re: grouped predictors
In this inference run, `r length(IN$priors)` sets of priors were used.
These are the names:
```{r, echo=FALSE}
names(IN$priors)
```
These are the details regarding the grouping of predictors given the prior `r p.name`.
```{r, echo=FALSE}
gp <- IN$grouped.pred[[p.name]]
```
A total of `r length(gp$pred.has.na)` predictors contained NA and were removed.
A total of `r length(gp$pred.is.const)` predictors were constant and were removed.
A total of `r length(unique(unlist(gp$pred.groups)))` predictors formed `r length(gp$pred.groups)` groups.
These are the groups and the members:
```{r, echo=FALSE}
gp$pred.groups
```

# Re: prior
These are details rearding the prior with the name `r names(IN$priors)[1]` after grouping predictors.
```{r}
table(p.mat)
dim(p.mat)

# table of out-degree and counts
out.vec <- apply(p.mat != 0, 2, sum)
table(out.vec)
# show how many regulators (TFs) have targets
table(out.vec > 0)

# print the regulators with the most targets
mt <- order(out.vec, decreasing=TRUE)[1:5]
data.frame(colnames(p.mat)[mt], out.vec[mt])

# table of in-degree and counts
in.vec <- apply(p.mat != 0, 1, sum)
table(in.vec)
# show how many targets have regulators
table(in.vec > 0)

# print the targets with the most regulators
mt <- order(in.vec, decreasing=TRUE)[1:5]
data.frame(rownames(p.mat)[mt], in.vec[mt])

# print some network statisctics
net.stats(p.mat)

# overlap of prior and final network (beta sign)
# only use TFs and targets in the prior
rows <- in.vec > 0
cols <- out.vec > 0

overlap.tab <- table(as.vector(abs(beta.sign)[rows, cols] >= BETA.SIGN.TH), as.vector(p.mat[rows, cols] != 0))
overlap.tab
fisher.test(overlap.tab, alternative='greater')
# consider sign of interactions
table(as.vector(abs(beta.sign)[rows, cols] >= BETA.SIGN.TH) * sign(as.vector(beta.sign[rows, cols])), as.vector(sign(p.mat[rows, cols])))

# overlap of prior and final network (explained variance)
overlap.tab <- table(as.vector(var.exp[rows, cols]) >= VAR.EXP.TH, as.vector(p.mat[rows, cols] != 0))
overlap.tab
fisher.test(overlap.tab, alternative='greater')

```


# Re: AUPR

```{r}
source('/home/ch1421/Projects/Inferelator/R_scripts/evaluate.R')
cc.aupr <- aupr(comb.confs, p.mat, eval.on.subset=TRUE)
cat('AUPR is', cc.aupr, '\n')

```






